Notes

### 2020-09-25 supCLT-ind-JAP.tex
Update supCLT-ind-JAP.tex

	We now recall some notation and basic facts from \cite{RenSongSunZhao2019Stable}.
	We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
	Define $P^{\alpha}_t f(x) := e^{\alpha t} P_t f(x) = \Pi_x [e^{\alpha t}f(\xi_t)]$ for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
	It is known that $\mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)$ for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
	The OU process $\xi$ has an invariant probability on $\mathbb R^d$:
\begin{align}
  	\varphi(x)\mathrm dx
  	:=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)\mathrm dx.
\end{align}
	Let $L^2(\varphi)$ be the Hilbert space with inner product
\begin{align}
  	\langle f_1, f_2 \rangle_{\varphi}
  	:= \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) \mathrm dx, \quad f_1,f_2 \in L^2(\varphi).
\end{align}
	Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
	It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.	
		The eigenfunctions of $L$ consists a family of polynomials $\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of $L^2(\varphi)$.
%	And for each $p\in \mathbb Z_+^d$, 
For each $p\in \mathbb Z_+^d$, 
$\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $b|p|$, where $|p|:= \sum_{k=1}^d p_k$.
	For each function $f\in L^2(\varphi)$, define the order of $f$ as
$\kappa_f
  	:= \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}$
with the convention that $\inf\emptyset=\infty.$

	For $p\in \mathbb{Z}_+^d$, define
$H_t^p
    	:= e^{-(\alpha-|p|b)t}X_t(\phi_p), t\geq 0.$
	For each $u \neq -1$, we write $\tilde u = u/(1+ u)$.
	We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} that
	for any
	$\mu\in \mathcal M_c(\mathbb R^d)$, $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale.
	Furthermore, if $\alpha \tilde \beta>|p|b$, then for every $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
	thus $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
%We will write $H^0_t$ and $H^0_\infty$ as $H^0_t$ and $H_\infty$, respectively.
We will write $H^0_t$ and $H^0_\infty$ as $H_t$ and $H_\infty$, respectively.

@@

\section{Proof of main result}
\label{proofs of main results}
	We first make some preparations before proving Theorem \ref{thm:M}.
	For every $t\geq 0$ and $f\in \mathcal P$, define
\[
  	Z_t f
  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)\mathrm ds,
  	\quad \Upsilon^f_t
   	:= \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}.
\]
	Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of 
%	the limit of $\Upsilon^f_t$.
the weak limit of $\Upsilon^f_t$.
	For $g = g_\mathrm s + g_\mathrm c + g_\mathrm l\in \mathcal P$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$, we define $\overline {\mathcal P}_g:= \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$, where $T_n$ is the operator defined in \eqref{e:Tt}.
	The following Lemma \ref{lem:P:R} can be proved using 
%	a similar argument used in the proof of 
an argument similar to that used in the proof of 
	\cite[Lemma 2.9]{RenSongSunZhao2019Stable}. We omit the details here.
\begin{lem}
\label{lem:P:R}
	For any $g\in \mathcal P$ there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
\end{lem}

	The following result is a generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable}, whose proof is similar to that of \cite[Proposition 3.5]{RenSongSunZhao2019Stable},
%		with using Lemma \ref{lem:P:R} above instead of Lemma 2.9 in \cite{RenSongSunZhao2019Stable}.
with Lemma \ref{lem:P:R} replacing the role of \cite[Lemma 2.9]{RenSongSunZhao2019Stable}.
	Let $(\mathscr F_t)_{t\geq 0}$ be the natural filtration of $X$.
	\begin{prop}
\label{thm:Key}
	For any $\mu \in \mathcal M_c(\mathbb R^d)$  and $g \in \mathcal P$, there exist $C,\delta>0$ such that for all $t\geq 1$ and $f \in \overline{\mathcal P}_g$, we have
\[
	\mathbb P_\mu
	\Big[ \big|\mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ]  \big|\Big]
	\leq C e^{- \delta t}.
\]
\end{prop}

@@

	In the remainder of this section, we  fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$,  $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$.
	For every $t\geq 1$, define
\begin{align}
	R(t)
	&:=\Big( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}\Big),
        \\R'(t)
    &=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
        \\& :=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
\end{align}
where $T_k$ is the operator defined in 
%\eqref{e:Tt} and $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} 
\eqref{e:Tt}, $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} 
with $f$ replaced with $f_\mathrm l$, $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and $\tilde f_\mathrm l := \sum_{p\in \mathbb Z^d_+: \alpha\tilde\beta>|p|b}e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
	The following result is a special case of Theorem \ref{thm:M}.
\begin{thm}\label{thm: II}
	Under $\mathbb{\widetilde{P}}_{\mu}$, $R(t) \xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
\end{thm}
\begin{proof}
	In this proof, we always work under $\mathbb{\widetilde{P}}_{\mu}$.
	According to the proof of 
%	Theorem 1.6 in \cite{RenSongSunZhao2019Stable}, and the fact that the convergence in
\cite[Theorem 1.6]{RenSongSunZhao2019Stable} and the fact that the convergence in
 probability of random vectors to the zero vector is equivalent to the convergence of each components of the random vectors to zero, we have
\[
	R(t)-R'(t)
	\xrightarrow[t\to \infty]{\text{in probability}} 0.
\]
	With the help of Slutsky's theorem, what is left to show is that,
\begin{equation} \label{lem:UOT}
	R'(t)
	\xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
\end{equation}

	Now we prove \eqref{lem:UOT}.
	Since $\Upsilon_t^f$ is linear in $f$, for each $t\geq 1$,
\[
        \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l} R'_j(t)\Big)\Big]
	= \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\sum_{k=0}^{\lfloor t-\ln t \rfloor}\Upsilon_{t-k-1}^{T_k(\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c})}\Big)\exp\Big(i\sum_{k=0}^{\lfloor t^2 \rfloor}\Upsilon_{t+k}^{-T_k\tilde{f}_{\mathrm l}}\Big)\Big].
\]
	Note that $\{T_k(\tilde f_\mathrm s + t^{\tilde\beta - 1}\tilde f_{\mathrm c}):k\in \mathbb Z_+, t\geq 1\}\subset \overline{\mathcal P}_{\tilde f_\mathrm s + \tilde f_{\mathrm c}}$ and $\{-T_k\tilde{f}_{\mathrm l}: k\in \mathbb Z_+\}\subset \overline{\mathcal P}_{\tilde f_\mathrm l}$.
	Therefore, we can use Proposition \ref{cor:MI} with $f$ 
%	taking as $\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g$ taking as 
taken as $\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g$ taken as
	$\tilde{f}_{\mathrm l}$
	%, and get that there exist $C_1,\delta_1 > 0$ such that for every $t>e$ (which implies $t\geq \lfloor t - \ln t\rfloor +1$),
	to get that there exist $C_1,\delta_1 > 0$ such that for every $t>e$ (which implies $t\geq \lfloor t - \ln t\rfloor +1$),
\begin{align}
       &\begin{multlined}
  	\bigg|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}R'_j(t)\Big)\Big] - 
  	\\ \exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \big\langle Z_1\big(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_{\mathrm c})\big), \varphi \big\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_{\mathrm l}),\varphi\rangle\Big)\bigg|
  	\end{multlined}
      \\ &\leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}.
\end{align}
	We claim that
\begin{align}
\label{eq:UOT.1}
	&\lim_{t\rightarrow\infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}\big \langle Z_1\big(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c)\big), \varphi\big\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big)
	\\& =\exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
\end{align}
	Given this claim, we have
\[
	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l} R'_{j}(t)\Big)\Big]
	\xrightarrow[t\to \infty]{} \exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
\]
	Since $R'_{j}(t)$ are linear 
	 in $f_j \in \mathcal C_j~(j=\mathrm s,\mathrm c,\mathrm l)$, replacing $f_j$ with $\theta_j f_j$, we immediately get \eqref{lem:UOT}.

>>>>

	We now recall some notation and basic facts from \cite{RenSongSunZhao2019Stable}.
	We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
	Define $P^{\alpha}_t f(x) := e^{\alpha t} P_t f(x) = \Pi_x [e^{\alpha t}f(\xi_t)]$ for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
	It is known that $\mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)$ for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
	The OU process $\xi$ has an invariant probability on $\mathbb R^d$:
\begin{align}
  	\varphi(x)\mathrm dx
  	:=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)\mathrm dx.
\end{align}
	Let $L^2(\varphi)$ be the Hilbert space with inner product
\begin{align}
  	\langle f_1, f_2 \rangle_{\varphi}
  	:= \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) \mathrm dx, \quad f_1,f_2 \in L^2(\varphi).
\end{align}
	Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
	It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.	
		The eigenfunctions of $L$ consists a family of polynomials $\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of $L^2(\varphi)$.
For each $p\in \mathbb Z_+^d$, 
$\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $b|p|$, where $|p|:= \sum_{k=1}^d p_k$.
	For each function $f\in L^2(\varphi)$, define the order of $f$ as
$\kappa_f
  	:= \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}$
with the convention that $\inf\emptyset=\infty.$

	For $p\in \mathbb{Z}_+^d$, define
$H_t^p
    	:= e^{-(\alpha-|p|b)t}X_t(\phi_p), t\geq 0.$
	For each $u \neq -1$, we write $\tilde u = u/(1+ u)$.
	We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} that
	for any
	$\mu\in \mathcal M_c(\mathbb R^d)$, $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale.
	Furthermore, if $\alpha \tilde \beta>|p|b$, then for every $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
	thus $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
We will write $H^0_t$ and $H^0_\infty$ as $H_t$ and $H_\infty$, respectively.

@@

\section{Proof of main result}
\label{proofs of main results}
	We first make some preparations before proving Theorem \ref{thm:M}.
	For every $t\geq 0$ and $f\in \mathcal P$, define
\[
  	Z_t f
  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)\mathrm ds,
  	\quad \Upsilon^f_t
   	:= \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}.
\]
	Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of 
the weak limit of $\Upsilon^f_t$.
	For $g = g_\mathrm s + g_\mathrm c + g_\mathrm l\in \mathcal P$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$, we define $\overline {\mathcal P}_g:= \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$, where $T_n$ is the operator defined in \eqref{e:Tt}.
	The following Lemma \ref{lem:P:R} can be proved using 
an argument similar to that used in the proof of 
	\cite[Lemma 2.9]{RenSongSunZhao2019Stable}. We omit the details here.
\begin{lem}
\label{lem:P:R}
	For any $g\in \mathcal P$ there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
\end{lem}

	The following result is a generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable}, whose proof is similar to that of \cite[Proposition 3.5]{RenSongSunZhao2019Stable},
with Lemma \ref{lem:P:R} replacing the role of \cite[Lemma 2.9]{RenSongSunZhao2019Stable}.
	Let $(\mathscr F_t)_{t\geq 0}$ be the natural filtration of $X$.
	\begin{prop}
\label{thm:Key}
	For any $\mu \in \mathcal M_c(\mathbb R^d)$  and $g \in \mathcal P$, there exist $C,\delta>0$ such that for all $t\geq 1$ and $f \in \overline{\mathcal P}_g$, we have
\[
	\mathbb P_\mu
	\Big[ \big|\mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ]  \big|\Big]
	\leq C e^{- \delta t}.
\]
\end{prop}

@@

	In the remainder of this section, we  fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$,  $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$.
	For every $t\geq 1$, define
\begin{align}
	R(t)
	&:=\Big( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}\Big),
        \\R'(t)
    &=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
        \\& :=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
\end{align}
where $T_k$ is the operator defined in 
\eqref{e:Tt}, $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} 
with $f$ replaced with $f_\mathrm l$, $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and $\tilde f_\mathrm l := \sum_{p\in \mathbb Z^d_+: \alpha\tilde\beta>|p|b}e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
	The following result is a special case of Theorem \ref{thm:M}.
\begin{thm}\label{thm: II}
	Under $\mathbb{\widetilde{P}}_{\mu}$, $R(t) \xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
\end{thm}
\begin{proof}
	In this proof, we always work under $\mathbb{\widetilde{P}}_{\mu}$.
	According to the proof of 
\cite[Theorem 1.6]{RenSongSunZhao2019Stable} and the fact that the convergence in
 probability of random vectors to the zero vector is equivalent to the convergence of each components of the random vectors to zero, we have
\[
	R(t)-R'(t)
	\xrightarrow[t\to \infty]{\text{in probability}} 0.
\]
	With the help of Slutsky's theorem, what is left to show is that,
\begin{equation} \label{lem:UOT}
	R'(t)
	\xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
\end{equation}

	Now we prove \eqref{lem:UOT}.
	Since $\Upsilon_t^f$ is linear in $f$, for each $t\geq 1$,
\[
        \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l} R'_j(t)\Big)\Big]
	= \widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i\sum_{k=0}^{\lfloor t-\ln t \rfloor}\Upsilon_{t-k-1}^{T_k(\tilde{f_\mathrm s}+t^{\tilde{\beta}-1} \tilde{f}_{\mathrm c})}\Big)\exp\Big(i\sum_{k=0}^{\lfloor t^2 \rfloor}\Upsilon_{t+k}^{-T_k\tilde{f}_{\mathrm l}}\Big)\Big].
\]
	Note that $\{T_k(\tilde f_\mathrm s + t^{\tilde\beta - 1}\tilde f_{\mathrm c}):k\in \mathbb Z_+, t\geq 1\}\subset \overline{\mathcal P}_{\tilde f_\mathrm s + \tilde f_{\mathrm c}}$ and $\{-T_k\tilde{f}_{\mathrm l}: k\in \mathbb Z_+\}\subset \overline{\mathcal P}_{\tilde f_\mathrm l}$.
	Therefore, we can use Proposition \ref{cor:MI} with $f$ 
taken as $\tilde{f_\mathrm s}+ \tilde{f}_{\mathrm c}$ and $g$ taken as
	$\tilde{f}_{\mathrm l}$
	to get that there exist $C_1,\delta_1 > 0$ such that for every $t>e$ (which implies $t\geq \lfloor t - \ln t\rfloor +1$),
\begin{align}
       &\begin{multlined}
  	\bigg|\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l}R'_j(t)\Big)\Big] - {}
  	\\ \exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \big\langle Z_1\big(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_{\mathrm c})\big), \varphi \big\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_{\mathrm l}),\varphi\rangle\Big)\bigg|
  	\end{multlined}
      \\ &\leq C_1 e^{-\delta_1(t - \lfloor t - \ln t\rfloor)}.
\end{align}
	We claim that
\begin{align}
\label{eq:UOT.1}
	&\lim_{t\rightarrow\infty}\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}\big \langle Z_1\big(T_{k}(\tilde f_\mathrm s+t^{\tilde{\beta}-1}\tilde{f}_\mathrm c)\big), \varphi\big\rangle \Big)\exp\Big(\sum_{k=0}^{\lfloor t^2 \rfloor}\langle Z_1(-T_k\tilde{f}_\mathrm l),\varphi\rangle\Big)
	\\& =\exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
\end{align}
	Given this claim, we have
\[
	\widetilde{\mathbb P}_{\mu}\Big[\exp\Big(i \sum_{j=\mathrm s,\mathrm c,\mathrm l} R'_{j}(t)\Big)\Big]
	\xrightarrow[t\to \infty]{} \exp(m[f_\mathrm s]+m[f_\mathrm c]+m[-f_\mathrm l]).
\]
	Since $R'_{j}(t)$ are linear 
	 in $f_j \in \mathcal C_j~(j=\mathrm s,\mathrm c,\mathrm l)$, replacing $f_j$ with $\theta_j f_j$, we immediately get \eqref{lem:UOT}.
